Practical Hilbert space approximate Bayesian Gaussian processes for probabilistic programming

### 2022-08-15 Paper/Manuscript_Stats&Comp/reply_letter_2nd_STCO.tex
updated response letter submitted

%We are grateful for your valuable comments and suggestions, which have been very helpful to improve the paper, and more generally for your time you have dedicated to reviewing it. We would also like to thank you for the additional feedback on some of our responses.

%\subsubsection*{R\#1 General comment and feedback for the authors}
%
%\textbf{Overall, the paper has clearly improved from the original submission and the revision addresses all of my major revision requests adequately. I still think the paper is a bit borderline in terms of the technical contribution itself, but the revised version reads better, is more clear on the limitations, clarifies a few open issues, and the experimental section has been improved. In particular, the experimental section is now very extensive and provides rich information about the practical use and limitations of the approach. The paper certainly has potential for impact as a practical guide and tools for using HSGP and now is clearly more suitable for publication. I do not have any major comments for the paper and would be happy to see it accepted in current form.}
%
%\textbf{Quick feedback on (some of) the author responses:}
%
%\textbf{1. Apologies for skipping the statement on brms integration. I agree it is valuable as it makes the contribution more accessible for a broad audience that might not be interested in the technical details.}
%
%\textbf{3. This resolves by remark well. Good addition that will help practitioners and can be implemented directly for the software as default criteria.}
%
%\textbf{4. I appreciate the effort of extending the treatment. I still have a bit of an issue of how this needs to be done separately for each possible kernel and the implications that has on general probabilistic programming environments where part of the value of the tool is in providing extreme flexibility, but I do agree that for practical uses e.g. with brms the set of kernels you now provided is useful and likely to cover most user needs.}
%
%\textbf{5. Fair enough; I certainly agree some (if not many) practitioners would fail to do this properly.}
%
%\textbf{6-8. I think the experimental section indeed reads better now and is overall very extensive and detailed.}
%
%\textbf{9. By mostly negative results I meant that the value of the approach is not obvious and hence a practitioner would get the impression that investigating the value of HSGP for higher-dimensional cases would not be worthwhile since the gain would likely be small compared to the effort. Apologies for the slightly confusing statement, since I agree you do show some advantage on the Leukemia data. The new experiments on simulated data make this aspect more clear.}
%
%\textbf{Finally, a quick comment related to R\#2 Comment \#3: I agree here with the authors that empirical comparison against alternative inference techniques is not necessary and would not really make the paper stronger either.}

@@

%The authors think that the rest of the figures look good in their current form.

@@

%Although that has been said extensively throughout the paper, we have added a remark in Section 4.8.1 and a note at the end of Section 4.5.1, as suggested by the reviewer, which we also think can help to make it more clear.

@@

%We are grateful for your valuable comments and suggestions, which have been very helpful to improve the paper, and more generally for your time you have dedicated to reviewing it.

@@

%We included the solution of a spline model (a model related to the GP/HSGP model) only in case study I, with no other intention than to show, beside the GP and HSGP solutions, the solution of a spline model, which has similar (of the same order) computational cost and limitations in multidimensional cases. It can be seen that a basic formulation of a spline model causes significantly worse extrapolation accuracy.

@@

We apologize for creating confusion with our notation here. {\color{blue}The diagnostic Figure~5 and equations (19--24) work with a normalized lengthscale, i.e., a lengthscale $\ell$ normalized by the zero-mean, symmetric interval $S$ which contains the inpus values $x_i$ ($\ell/S$), so the conclusions can be easily referred to any specific scale of the input domain. In concrete in step A.1 in Section 4.5.1 we recommend values for a first guess of the lengthscale based on the normalized lengthscale. We have now clarified the role and use of the normalized lengthscale relative to $S$ throughout the paper.}

%We work with a normalized lengthscale, i.e., a lengthscale $\ell$ relative to the half-range ($S$) of the input domain ($\ell/S$), so the conclusions can be easily referred to any specific scale of the input domain. We have now clarified the notation by using different symbols for lengthscale and normalized lengthscale throughout the paper.

@@

%\noindent \hdashrule{12.5cm}{0.2pt}{2mm 1pt}

%\nobibliography{references}

>>>>

@@

@@

@@

@@

@@

We apologize for creating confusion with our notation here. The diagnostic Figure~5 and equations (19--24) work with a normalized lengthscale, i.e., a lengthscale $\ell$ normalized by the zero-mean, symmetric interval $S$ which contains the inpus values $x_i$ ($\ell/S$), so the conclusions can be easily referred to any specific scale of the input domain. In concrete in step A.1 in Section 4.5.1 we recommend values for a first guess of the lengthscale based on the normalized lengthscale. We have now clarified the role and use of the normalized lengthscale relative to $S$ throughout the paper.

@@
